In this section, the JSD-MP problem is formulated as a MILP model. First the
variables of the model are introduced, then the constraints are discussed, and
finally the objective is presented.

The variables are listed in Table~\ref{tbl:variables}. \(x_r\) is a binary
variable for the acceptance of demand \(r \in R\). The integer variable
\(y_{it}\) is the number of VNFs of type \(t \in T\) on server \(i\). The binary
variable \(z^t_{vi}\) indicates whether an instance of VNF type \(t\) serves node
\(v\) on server \(i\). The integer variable \(\bar{y}_i\) is the number of VNFMs
placed on server \(i\), and the binary variable \(\bar{z}_{ri}\) represents the
VNFM assignment of a chain. Finally, \(\pi^{(u,v)}_{ij}\) and \(\bar{\pi}^v_{ij}\)
are binary variables indicating that virtual link \((u,v)\) is mapped on physical
link \((i,j)\) and that link \((i,j)\) is used to manage VNF \(v\), respectively.

\begin{table}[H]
\caption{Variables.}
\label{tbl:variables}
\small
\begin{tabularx}{\textwidth}{cX}
\toprule
\textbf{Variable} & \textbf{Description} \\
\midrule
\(x_r\) & 1 if the SFC request \(r\) is accepted; otherwise 0 \\
\(y_{it}\) & number of VNF instances of type \(t \in T\) set up on server \(i \in V^p\) \\
\(z^t_{vi}\) & 1 if VNF node \(v \in \bigcup_{r=1}^{R} V^s_r\) is served by a VNF instance of type \(t \in T\) on server \(i \in V^p\) \\
\(\bar{y}_i\) & number of VNFMs set up on server \(i \in V^p\) (each with its capacity and license fee) \\
\(\bar{z}_{ri}\) & 1 if SFC \(r\) is assigned to a VNFM on server \(i \in V^p\) \\
\(\pi^{(u,v)}_{ij}\) & 1 if virtual link \((u,v)\) is routed on physical link \((i,j)\) \\
\(\bar{\pi}^v_{ij}\) & 1 if the management of VNF node \(v\) is routed on physical link \((i,j)\) \\
\bottomrule
\end{tabularx}
\end{table}

Each node has limited installed memory; each VNF instance (by its type) and each
VNFM uses a specific amount. Equation~\eqref{eq:node-memory} limits the used
memory of each node by its installed memory.

\begin{equation}\label{eq:node-memory}
\sum_{t \in T} y_{it}\, m^s_t + \bar{y}_i\, m^m \le m^p_i \quad \forall i \in V^p
\end{equation}

Each node has limited processing power in CPU cores.
Equation~\eqref{eq:node-cpu} limits the used processing power of each node by its
installed CPUs.

\begin{equation}\label{eq:node-cpu}
\sum_{t \in T} y_{it}\, c^s_t + \bar{y}_i\, c^m \le c^p_i \quad \forall i \in V^p
\end{equation}

If a chain's node is served on a physical node, a VNF instance must be set up on
it. Equation~\eqref{eq:service-place} controls this relationship.

\begin{equation}\label{eq:service-place}
\sum_{v \in \bigcup_{r=1}^{R} V^s_r} z^t_{vi} \le y_{it}
\quad \forall i \in V^p,\ \forall t \in T
\end{equation}

Equations~\eqref{eq:service} and \eqref{eq:manager} accept a chain only if all of
its nodes are placed on physical servers and it has an assigned VNFM.

\begin{equation}\label{eq:service}
x_r = \sum_{t \in T} \sum_{i \in V^p} z^t_{vi}
\quad \forall v \in V^s_r,\ \forall r \in R
\end{equation}

\begin{equation}\label{eq:manager}
x_r = \sum_{i \in V^p} \bar{z}_{ri} \quad \forall r \in R
\end{equation}

Equation~\eqref{eq:manager-capacity} limits manager capacity.

\begin{equation}\label{eq:manager-capacity}
\sum_{r \in R} \bar{z}_{ri} \cdot |V^s_r| \le \kappa \cdot \bar{y}_i
\quad \forall i \in V^p
\end{equation}

Equation~\eqref{eq:type} assures each chain's node is served by a VNF of its type.

\begin{equation}\label{eq:type}
z^t_{vi} \le \tau(v, t)
\quad \forall i \in V^p,\ \forall t \in T,\ \forall v \in \bigcup_{r \in R} V^s_r
\end{equation}

Each physical server has a set of servers that cannot manage it.
Equation~\eqref{eq:mgmt-relationship} represents this.

\begin{equation}\label{eq:mgmt-relationship}
\begin{aligned}
& 1 - z^t_{vi} + \bar{z}_{rj} = 0, \\
& \forall i, j \in V^p \text{ with } \eta_{i,j} = 1,\ \forall r \in R,\ \forall v \in V^s_r,\ \forall t \in T
\end{aligned}
\end{equation}

Equations~\eqref{eq:flow} and \eqref{eq:mgmt-flow} express flow conservation on
service and management links, respectively.

\begin{equation}\label{eq:flow}
\begin{aligned}
& \sum_{(i,j) \in E^p} \pi^{(u,v)}_{ij} - \sum_{(j,i) \in E^p} \pi^{(u,v)}_{ji} = \sum_{t \in T} z^t_{ui} - \sum_{t \in T} z^t_{vi}, \\
& \forall i \in V^p,\ (u,v) \in E^s_r,\ r \in R
\end{aligned}
\end{equation}

\begin{equation}\label{eq:mgmt-flow}
\begin{aligned}
& \sum_{(i,j) \in E^p} \bar{\pi}^v_{ij} - \sum_{(j,i) \in E^p} \bar{\pi}^v_{ji} = \sum_{t \in T} z^t_{vi} - \bar{z}_{ri}, \\
& \forall i \in V^p,\ v \in V^s_r,\ r \in R
\end{aligned}
\end{equation}

Equation~\eqref{eq:link-bw} limits the consumed bandwidth of each link by its
capacity.

\begin{equation}\label{eq:link-bw}
\begin{aligned}
& \sum_{v \in \bigcup_{r \in R} V^s_r} \bar{\pi}^v_{ij} \cdot b^m + \sum_{r \in R} \sum_{(u,v) \in E^s_r} \pi^{(u,v)}_{ij} \cdot b^s_{(u,v),r} \le b^p_{ij}, \\
& \forall (i,j) \in E^p
\end{aligned}
\end{equation}

Equation~\eqref{eq:radius} controls the management radius.

\begin{equation}\label{eq:radius}
\sum_{(i,j) \in E^p} \bar{\pi}^v_{ij} \le \rho
\quad \forall v \in \bigcup_{r \in R} V^s_r
\end{equation}

The objective is to maximize the profit from placing chains:

\begin{equation}\label{eq:objective}
\max \sum_{r \in R} c_r\, x_r - \sum_{i \in V^p} \phi \cdot \bar{y}_i
\end{equation}

The problem is an ILP and can be reduced to bin packing, so it is NP-hard.
