%=================================================================
% Joint Service Chain Deployment and Manager Placement in NFV
% MDPI (Future Internet) LaTeX manuscript.
% Uses the MDPI class in Definitions/ (download the latest from
% https://www.mdpi.com/authors/latex before final submission).
%=================================================================
\documentclass[futureinternet,article,submit,pdftex,moreauthors]{Definitions/mdpi}

% Extra packages (most are already loaded by the MDPI class: amsmath, float,
% booktabs, graphicx, multirow, xcolor, hyperref).
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algpseudocode}

\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2026}
\copyrightyear{2026}
\history{Received: ; Accepted: ; Published: }

%=================================================================
\Title{Joint Service Chain Deployment and Manager Placement in NFV}

\Author{Parham Alvani $^{1}$ and Bahador Bakhshi $^{1,}$*}

\AuthorNames{Parham Alvani and Bahador Bakhshi}

\address{%
$^{1}$ \quad Amirkabir University of Technology, Tehran, Iran;
parham.alvani@aut.ac.ir (P.A.); bbakhshi@aut.ac.ir (B.B.)}

\corres{Correspondence: bbakhshi@aut.ac.ir}

\abstract{Network operators deploying service function chains (SFCs) with Network
Function Virtualization (NFV) must also provide each chain with a VNF Manager
(VNFM) under capacity, latency-radius, and co-location constraints. Most prior
work optimizes VNF placement first and assigns managers afterward. We show that
this \emph{disjoint} approach is not merely suboptimal but frequently
\emph{infeasible}: management-blind VNF layouts strand whole chains because no
admissible manager exists for the chosen placement. We formulate the joint SFC
deployment and VNFM placement problem (JSD-MP) as an Integer Linear Program,
show it is NP-hard, and propose MASMAN, a polynomial-time heuristic that makes
VNF placement management-aware (a Viterbi-style dynamic program) and then
consolidates managers with Tabu search. Against an exact CPLEX solver---which
already exhausts memory at around a dozen chains---the heuristic stays within
roughly 18\% of the optimal revenue while scaling to hundreds of chains. Finally,
we characterize
\emph{when} joint placement matters: its benefit is a feasibility effect that
appears precisely when management constraints bind, and is negligible under
slack management or when raw compute saturates the network.}

\keyword{network function virtualization; service function chaining; VNF
placement; VNF manager placement; joint optimization; integer linear
programming; heuristic; feasibility}

\begin{document}

\section{Introduction}\label{sec:introduction}
\input{introduction}

\section{Related Work}\label{sec:related-works}
\input{related-works}

\section{System Model and Problem Statement}\label{sec:system-model}
\input{system}

\section{Problem Formulation}\label{sec:formulation}
\input{formulation}

\section{Proposed Solution}\label{sec:solution}
\input{solution}

\section{Evaluation and Numerical Results}\label{sec:results}
\input{results}

\section{Conclusions}\label{sec:conclusion}
We considered, for the first time, the joint deployment of service function
chains and the placement of their VNF Managers (JSD-MP). We formulated the
problem as an ILP, showed its NP-hardness, and proposed MASMAN, a
polynomial-time heuristic that is management-aware during VNF placement and
consolidates managers with Tabu search. Our evaluation shows the heuristic stays
within roughly 18\% of the optimal revenue while scaling well beyond the reach of
the exact solver, and that the value of joint placement is a feasibility effect
that is large exactly when management constraints bind. Future work includes an
online variant in which requests arrive over time, reliability-aware manager
placement with backup managers, and tighter approximation guarantees for the
manager-placement subproblem (which is a capacitated facility-location problem
with a coverage radius).

\vspace{6pt}

\authorcontributions{Conceptualization, P.A. and B.B.; methodology, P.A. and
B.B.; software, P.A.; validation, P.A. and B.B.; formal analysis, P.A.;
investigation, P.A.; writing---original draft preparation, P.A.;
writing---review and editing, B.B.; supervision, B.B. All authors have read and
agreed to the published version of the manuscript.}

\funding{This research received no external funding.}

\conflictsofinterest{The authors declare no conflict of interest.}

\appendixtitles{yes}
\appendix
\section{Revenue Tables}\label{sec:revenue-appendix}
\input{appendix}

\reftitle{References}
\externalbibliography{yes}
\bibliography{references}

\end{document}
